Last glacial cycle glacier erosion potential in the Alps

### 2021-05-19 articles/erosion/response-referee2.md

TODO: discuss lithology, go through entire text?

> A further necessary geographical qualification concerns the misfit between
> simulated and actual glacier extent. The latter is well established from
> mapping of moraines. It is necessary to check Seguinot et al. (2018) to see
> that all the models predict too much ice in the southwest (south of 45° N)
> and far too much in the east (Sava, Drava, Mur, Enns and Traun valleys),
> while the EPICA models produce too little in the west (Rhône and Jura). I
> agree that this is probably because while the amount of precipitation is
> changed, the spatial pattern is not: thus the orographic effect of ice
> build-up increasing precipitation shadow, and the circulation changes due to
> southward shift of westerlies at LGM, are not included. To make this paper
> more self-contained, a brief mention of the 2018 evaluation is in order.
> Once a more realistic LGM precipitation pattern is accepted, future modelling
> might use gradations between that and the present pattern as a function of
> temperature.

The LGM outline was added on Fig. 2.

TODO: discuss shortly the discrepancy in "climate sensitivity".

@@

> The text is short and pithy, so there is space for some extension. There are
> a few missed opportunities, and some incompleteness in the presentation. In
> detail I suggest the following improvements:

## Specific comments - Text:

> The 1 km resolution of the modelling is clearly important, so it is strange
> that the first mention is on p.11. Although it is very demanding of computer
> time, it is still (as admitted) not adequate to represent cirques (averaging
> of the order of 700 m across). Even stranger, there is no mention of the DEM
> used (it was SRTM in the 2018 paper). This information should be provided in
> section 2, p. 3-4.

TODO: The input SRTM topography was mentioned in [...] and in the caption of
Fig. 2.

@@

> In lines 206-209, the point about trimlines, relating them to
> time-transgressive erosion, is well taken. But they represent the integrated
> effect of many phases of glacial erosion (as noted on 223-224), not
> necessarily just from recessional phases.

## - Figures:

> In Fig. 3 is almost impossible to follow the brown lines, unless advancing
> and retreating parts of lines are distinguished (e.g. by colour). (The ice
> volume video may help out.)  Also: keep to ‘potential erosion volume’. The
> pale brown bars show a decline in annual erosion volume with ice volumes over
> 1.8 cm s.l.e., stronger than is implied in line 110 of the text – it is more
> than ‘slight’.

We applied different colours for periods of increasing and decreasing ice
volume. This actually strikingly highlights the two different regimes. Thank
you for the suggestion. The label was changed to 'potential annual erosion
volume'.

TODO: not so slight decrease.

### 2021-05-19 articles/erosion/alps-erosion.tex
Use advance and retreat colors in evol figure.

    \begin{figure}
      \centerline{\includegraphics{alpero_evolution}}
      \caption{%
        Modelled annual (domain-integrated) erosion volume (light brown) and 1-ka
        running mean (dark brown) in relation to modelled total ice volume in
        centimetres of sea-level equivalent.}
      \label{fig:evolution}
    \end{figure}

>>>>

    \begin{figure}
      \centerline{\includegraphics{alpero_evolution}}
      \caption{%
        Modelled annual (domain-integrated) erosion volume (light curves) and 1-ka
        running mean (dark curves) in relation to modelled total ice volume in
        centimetres of sea-level equivalent. Blue indicates increasing ice
        volume and brown decreasing ice volume.}
      \label{fig:evolution}
    \end{figure}
